Symbiont shuffling linked to differential photochemical dynamics of *Symbiodinium* in three Caribbean reef corals

### 2017-11-01 analysis/analysis.Rmd
tidy

---
title: "Symbiont shuffling linked to differential photochemical efficiency of *Symbiodinium* in three Caribbean reef corals"
output: html_document
---

@@

# Get data frame with Mcav repeat bleaching data (=second bleaching)
Mc <- subset(alldata, BleachLvl2=="Heat" & Species=="Mc")
## Re-level Mcav data for merging with Ofav and Ssid data
## Set data after recovery from first bleaching to the "initial" factor levels
Mc$PropD.init <- Mc$PropD.recov  
Mc$MaxY.init <- Mc$MaxY.recov
## Set data after the second bleaching to the "bleached" factor levels
Mc$BleachLvl <- as.character(Mc$BleachLvl2)
Mc$PropD.bleach <- Mc$PropD.bleach2
Mc$MaxY.bleach <- Mc$MaxY.bleach2
## Set BleachLvl to "Med" to match Ofav and Ssid factor level
Mc$BleachLvl[Mc$BleachLvl=="Heat"] <- "Med"
## Set data after second recovery to the "recove#d95f02" factor levels
Mc$PropD.recov <- Mc$PropD.recov2
Mc$MaxY.recov <- Mc$MaxY.recov2

@@

```{r Fig2}

@@

```{r Fig3}
# Figure 3
png("figures/Fig3.png", width=7, height=3.5, units="in", res=300)
par(mfrow=c(1, 2), mar=c(3,3,1,1), mgp=c(1.5, 0.1, 0), tcl=0.2, cex.axis=0.8)
## Figure 3A: Final vs. initial proportion clade D
plot(NA, xlim=c(0,1), ylim=c(0,1), xaxs="i", yaxs="i",
     xlab="Prop. D1a before bleaching",
     ylab="Prop. D1a after recovery")
# Plot lines for low bleaching
with(subset(res.Low, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Low, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Low, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
abline(0,1, lty=1, lwd=0.5)
# Plot lines for Med bleaching
with(subset(res.Med, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Med, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Med, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
# Plot lines for High bleaching
with(subset(res.High, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.High, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.High, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
legend("bottomright", bty="n", lty=c(1,2,3), lwd=2, inset=c(0.05, 0),
       legend=c("7 days", "10 days", "14 days"), cex=0.7)
legend("bottomright", bty="n", pch=15, inset=c(0.04, 0.175),
       legend=c("Mcav", "Ssid", "Ofav"), cex=0.7, pt.cex=1.5, x.intersp=1.5,
       col=c("#d95f02", "#7570b3", "#1b9e77"))
#text(par("usr")[1]-par("mai")[2]/2, par("usr")[4], "A.", font=2, xpd=NA)
#text(-0.2, par("usr")[4], "A.", font=2, xpd=NA)
mtext("a", adj=-0.2, font=2)

@@

```{r Fig4}

@@

# Predict shuffling response based on relative Fv/Fm value and BleachLvl
## relative Fv/Fm at ambient temperatures ("normal") is perfectly correlated with relative Fv/Fm at stress temperatures ("stress") so only one variable can be used in model.  Or, should the slope of the Fv/Fm line be used, rather than the "relative difference"? (makes very little difference whether relative or slope is used.) *slope needs to be used because relative is different for diff BleachLvl levels, but slope is the same!

>>>>

---
title: "Symbiont shuffling linked to differential photochemical dynamics of *Symbiodinium* in three Caribbean reef corals"
output: html_document
---

@@

# Get data frame with Mcav repeat bleaching data (=second bleaching)
Mc <- subset(alldata, BleachLvl2=="Heat" & Species=="Mc")
## Re-level Mcav data for merging with Ofav and Ssid data
## Set data after recovery from first bleaching to the "initial" factor levels
Mc$PropD.init <- Mc$PropD.recov  
Mc$MaxY.init <- Mc$MaxY.recov
## Set data after the second bleaching to the "bleached" factor levels
Mc$BleachLvl <- as.character(Mc$BleachLvl2)
Mc$PropD.bleach <- Mc$PropD.bleach2
Mc$MaxY.bleach <- Mc$MaxY.bleach2
## Set BleachLvl to "Med" to match Ofav and Ssid factor level
Mc$BleachLvl[Mc$BleachLvl=="Heat"] <- "Med"
## Set data after second recovery to the "recovered" factor levels
Mc$PropD.recov <- Mc$PropD.recov2
Mc$MaxY.recov <- Mc$MaxY.recov2

@@

## Plot Figure 2
```{r Fig2}

@@

## Plot Figure 3
```{r Fig3}
# Figure 3
png("figures/Fig3.png", width=7, height=3.5, units="in", res=300)
par(mfrow=c(1, 2), mar=c(3,3,1,1), mgp=c(1.5, 0.1, 0), tcl=0.2, cex.axis=0.8)
## Figure 3A: Final vs. initial proportion clade D
plot(NA, xlim=c(0,1), ylim=c(0,1), xaxs="i", yaxs="i",
     xlab="Prop. D1a before bleaching",
     ylab="Prop. D1a after recovery")
# Plot lines for low bleaching
with(subset(res.Low, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Low, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Low, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
abline(0,1, lty=1, lwd=0.5)
# Plot lines for Med bleaching
with(subset(res.Med, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Med, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Med, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
# Plot lines for High bleaching
with(subset(res.High, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.High, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.High, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
legend("bottomright", bty="n", lty=c(1,2,3), lwd=2, inset=c(0.05, 0),
       legend=c("7 days", "10 days", "14 days"), cex=0.7)
legend("bottomright", bty="n", pch=15, inset=c(0.04, 0.175),
       legend=c("Mcav", "Ssid", "Ofav"), cex=0.7, pt.cex=1.5, x.intersp=1.5,
       col=c("#d95f02", "#7570b3", "#1b9e77"))
#text(par("usr")[1]-par("mai")[2]/2, par("usr")[4], "A.", font=2, xpd=NA)
#text(-0.2, par("usr")[4], "A.", font=2, xpd=NA)
mtext("a", adj=-0.2, font=2)

@@

## Plot Figure 4
```{r Fig4}

@@

# Predict shuffling response based on relative Fv/Fm value and BleachLvl
